### 2020-03-20 ChapterConclusion/chapterConclusion.tex
Updated: Conclusion proof-read

\section{Future Work}
Work will continue to carry out experiments to determine the effects that changing each of the aura tolerances has on the performance and scalability of AP. Future work will enable each tolerance value to be dynamic and the aura size could adapt with the changing conditions of the system. This would improve performance when factors are low and maintain correctness when factors are high.

@@

An alternative to just aura position and radius being sent over the network would be to send more details of the object projecting the aura. This could include bounding sphere and velocity and would allow the receiving server to determine the size of the aura. Under changing conditions, such as changes in latency the receiving server could dynamically change the size of the auras without the need for the sending server to send the new sizes of the auras.

@@

AP works on the principle that any two bodies that may be interacting are always being simulated on the same server. An alternative technique to this would be Cross-Boundary Interaction, as discussed in \ref{ConsideredSolutions}, allowing for bodies to interact across region boundaries i.e. objects that are being simulated on two different servers interacting over the network. There are likely various advantages and disadvantages of Cross-Boundary Interaction compared to Aura Projection, which could be explored and evaluated. The two solutions may have better performance in different situations (such as a large cluster on either side of a boundary) and a solutions which uses both techniques in different circumstances could be developed.

>>>>

\section{Future Work}
Work on AP will continue to be carried out, including experiments to determine the effects that changing each of the aura tolerances has on the performance and scalability of AP. Future work will enable each tolerance value to be dynamic and the aura size could adapt with the changing conditions of the system. This would improve performance when factors are low and maintain correctness when factors are high.

@@

An alternative to just the aura position and radius being sent over the network would be to send more details of the object projecting the aura. This could include bounding sphere and velocity and would allow the receiving server to determine the size of the aura. Under changing conditions, such as changes in latency the receiving server could dynamically change the size of the auras without the need for the sending server to send the new sizes of the auras.

@@

AP works on the principle that any two bodies that may be interacting are always being simulated on the same server. An alternative technique to this would be Cross-Boundary Interaction, as discussed in \ref{ConsideredSolutions}, allowing for bodies to interact across region boundaries i.e. objects that are being simulated on two different servers interacting over the network. There are likely various advantages and disadvantages of Cross-Boundary Interaction compared to Aura Projection, which could be explored and evaluated. The two solutions may have better performance in different situations (such as a large cluster on either side of a boundary) and a solution which uses both techniques under different circumstances could be developed.
